Automatic Hadith Graphs using Arabic Morphological Analysis

### 2011-06-02 tex/hadith.ijcnlp.tex
added tex file and modified fig

% File naaclhlt2010.tex
% Contact: nasmith@cs.cmu.edu
\documentclass[11pt]{article}
\usepackage{acl-hlt2011}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

%\title{Instructions for NAACL HLT 2010 Proceedings\Thanks{This...}}
\title{Hadith Narrator Chain Extraction using Arabic Morphological Analysis}

@@

\begin{document}
\maketitle
\begin{abstract}
A hadith in Islamic literature is a narration from the 
prophet Mohammad related by multiple narrators.
Establishing the authenticity of a hadith is an important task
in Islamic studies. 
Based on that Islamic scholars issue rules that affect the life
of people around the world. 
The literature lacks an automated exhaustive mechanism of 
authentication checks. 
This is currently manual work prone to error and almost
impossible to complete in the life time of a scholar due to the
large literature available. 
In this paper, we present a tool that uses 
an Arabic application-specific morphological analyzer 
to successfully automate the
analysis of three books of hadith selected 
arbitrarily and abstract 
each book into a graph of narrators related to each other. 
\end{quote}
\end{abstract}

\section{Introduction}
\novocalize

A \RL{.hady_t}~\footnote{In this document, 
we use the default ArabTeX transliteration style ZDMG.}
is a narration related to the prophet Mohammad
through a \RL{sanad} or a sequence of narrators. 
The collections of traditions are the second source of
jurisprudence after the \RL{qor'An} for all Islamic schools of thought. 
Figure~\ref{f:exhadith} shows an example \noArRL{.hady_t} in 
Arabic with its transliteration and translation. 
We show proper names in boxes connected
to form complex names of narrators. 
For example, 
\novocalize
\noTrRL{qtybT} is the first name 
of narrator $n_1$, and 
\noTrRL{s`yd} is the name of his father as 
the word \noTrRL{bn} (son of) indicates. 
The sequence of names from $n_1$ to $n_5$ 
constitutes the \noArRL{sanad} 
of the \noArRL{.hady_t}. 
The second part of the \noArRL{.hady_t} is the 
\RL{matn} (content) and constitutes the actual content 
of the tradition.

@@

In this paper, we present the hadith {narrator chain 
extractor using morphological analysis} (NaCEMA), 
a novel technique that automates
extracting the \noArRL{sanad} from the books of traditions 
into a diagram of chains of narrators. NaCEMA segments
a book into narrations, each narration into its \noArRL{matn} 
and its \noArRL{sanad}, 
and each sanad into its separate narrators. 
This work will lead to 
automate an exhaustive \noArRL{.hady_t} authentication 
effort in the future as we plan to 
automatically analyze the biography books.

@@

@@

%The rest of this paper is structured as follows. 
%In Section~\ref{sec:sarf}
%we discuss Sarf and illustrate it with a running example.
%We also explain how non-deterministic finite state Automata
%work. 
%In Section~\ref{sec:islamic} we present the hadith application. 
%We present our results in Section~\ref{sec:results}.
%In Section~\ref{sec:related}
%we compare NaCEMA to related work. 
%We conclude with future work in Section~\ref{sec:future}.

@@

%Several researchers~\cite{Hadithopaedia:08} attempted to automate 
%the analysis of the hadith literature. 
In this paper, we use Sarf to successfully automate the
analysis of three books of hadith selected 
arbitrarily~\cite{IbnHanbal,AlKulayni,AlTousi}\footnote{We obtained
  the digitized books from online sources such as 
  \href{http://www.yasoob.com/}{http://www.yasoob.com/} and 
  \href{http://www.al-eman.com/}{http://www.al-eman.com/}. }.
%  Our understanding is that those books are historical documents with 
 % public IP.}.
%\setcode{utf8}
%\begin{arabtext}
%حدثنا \emphasize{هشيم}، أخبرنا \emphasize{إسماعيل بن أبي خالد}،
% عن أبي إسحاق، عن سعيد بن جبير، قال كنا
%    مع ابن عمر رضي الله عنه حيث أفاض من
%    عرفات إلى جمع فصلى بنا المغرب ومضى
%\end{arabtext}
%\setcode{standard}
NaCEMA accepts a book as input
and segments it into a vector of hadiths. 
NaCEMA segments each hadith into its
sanad and matn parts. 
NaCEMA 
detects the chain of narrators in the sanad and 
the relation that links each narrator to his ancestor and 
predecessor in the chain. 
It also detects the full name of each narrator that is
composed of several proper names with connectors
in between.

@@

Intuitively, the controller reports a valid chain 
of narrators when a sequence of names
connected by narrator connectors appears. 
This includes the task of finding multi-word names
such as \RL{`bd alr.hmn} often appearing as ``run-on'' words.
The controller marks the beginning of the hadith with the beginning of 
the current proper name sequence,
and marks the end of the hadith with the beginning of the 
next proper name sequence. 
It detects the chain of narrators as the sequence itself.

%The controller also targets words that mean ``narrate'' when
%they appear between proper names. 
We illustrate the hadith controller 
in Figure~\ref{f:hadith}. 
The transitions are labeled by outputs generated from 
the Sarf morphological analyzer that correspond to 
part of speech (POS) tags. 
A NAME label denotes a proper name.
An NRC label denotes a narrator connector such as
\RL{`an} ``on behalf of'', \RL{.hada_t} ``narrated'', \RL{qaal} ``said'', 
\RL{'a_hbar} ``told'' or one of their morphological equivalents. 
An IBN label denotes the word \RL{ibn} ``the son of'' and is a name connector.
A NISBA is a possessive adjective that qualifies a person such 
as \RL{alma.sriy} ``the Egyptian''.

The symbol $\tau_{\mbox{NMC}}$ is a threshold
that corresponds to the number of tolerated name connectors 
that may occur between two names. %3
The symbol LIST$_{\mbox{NMC}}$ corresponds to the list 
of name connectors collected since the controller
started looping in the state NMC\_S. 
The symbol $\lambda_{\mbox{NMC}}$ is a parameter 
that corresponds to a relaxed tolerance measure that
the controller resorts to in case the words separating
two names were longer than $\tau_{\mbox{NMC}}$ but 
contained a name connector word such as IBN or NISBA.

The controller has four states that correspond to 
a position in text relative to the next sanad. 
State TEXT\_S is the initial state and denotes that
the controller is outside the context of a sanad.
The controller moves to state NAME\_S on
NAME.
State NRC\_S means that the controller is in the context
of a narrator name after Sarf reports an NRC.
State NMC\_S
indicates that the controller expects a name to appear within 
a tolerance threshold expressed by 
$\tau_{\mbox{NMC}}$ and $\lambda_{\mbox{NMC}}$.

Similarly, the NRC\_S state tolerates $\tau_{\mbox{NRC}}$ words 
before it gives up on its expectations. 
We reach the NAME\_S state only when a
valid NAME is detected and we leave when no more NAME's are detected.
The NRC\_S state can only be reached if an NRC is detected.
NMC\_S can only be reached from a NAME\_S state.
We used the values of 3, 5 and 5 for $\tau_{\mbox{NMC}}$, 
$\lambda_{\mbox{NMC}}$, and $\tau_{\mbox{NRC}}$ respectively.

@@

\begin{figure}[tb]
\center{
\resizebox{1.1\columnwidth}{!}
%{\includegraphics{figs/narrator_chain_output.pdf}}
{\includegraphics{figs/DAG_narrator.pdf}}
\caption{Narrator directed acyclic graph 
    extracted using NaCEMA }
\label{f:narrators} 
}
\end{figure}

The directed acyclic graph (DAG) 
in Figure~\ref{f:narrators} shows a partial order relation (POR) 
between narrators.
We automatically extracted the POR from the three books of 
hadith~\cite{IbnHanbal,AlKulayni,AlTousi}.
The nodes in boxes are the \RL{matn} of the hadith, 
and the other nodes are the narrators.
Given a set of chains of narrators similar to 
Figure~\ref{f:exhadith} we formed the DAG using graph algorithms 
that merged equal names in the chains. 
We compared the narrators together using a morphological
distance function. 
We considered each narrator to have several morphological 
components and we rewarded every morphological match with 
a small $\delta$. 
Then we applied a threshold $\tau$ to the sum of rewards
and decided the equality of the narrators. 
We omitted the details of the distance function for brevity.

@@

We ran our experiments using a dual core 2.66 Ghz 64-bit processor 
with 4GB of memory using a Linux operating system. 
We report our results in Table~\ref{t:hadithresallresults} on the 
three hadith books.
NaCEMA detected narrator chains and segmented the books 
correctly with a chain accuracy above 97\% and a narrator name
accuracy above 90\%
in all cases and across all the 1986 traditions in the three 
different books with different formats.

@@

The ``segmentation accuracy'' reports on the accuracy of 
segmentation of the book into separate hadiths.
We computed the metric manually by marking the beginning 
and end of a representative sample of hadiths in each 
book and compared that to the NaCEMA results. 
We used the same approach to compute all other accuracy measures.
The ``chain accuracy'' reflects the percentage of correct narrators 
covered by extracted chains.
The ``narrator name accuracy'' row reflects the percentage of 
correct proper names detected within
narrator structures.

@@

NaCEMA does not need a preprocessing step since 
it uses morphological analysis to process the text. 
While e-Narrator bases its analysis on the patterns 
of words that surround the narrator names, 
NaCEMA bases its analysis on the fact that narrator
names are likely to happen in localities with a high
number of proper names. 
NaCEMA uses the narrator connectors as helpers and
uses morphological analysis to compare the stems of
those words and thus NaCEMA avoids the problem of 
``parser noise words'' that e-Narrator faces. 
Even though we do not have access to the selected
90 traditions e-Narrator reports on, we claim
that NaCEMA outperforms e-Narrator as it works on
the full text of the presented hadith books
and reports a higher success rate.

@@

We presented NaCEMA, a narrator chain extractor
using morphological analysis. 
NaCEMA extracted narrator chains with above 90\% accuracy
from three different hadith books and generated 
directed acyclic graphs relating the narrators 
in a partial order relation.

>>>>

% File naaclhlt2010.tex
% Contact: nasmith@cs.cmu.edu
\documentclass[11pt]{article}
\usepackage{ijcnlp2011}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
%\DeclareMathOperator*{\argmax}{arg\,max}
%\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

%\title{Instructions for NAACL HLT 2010 Proceedings\Thanks{This...}}
\title{Automatic Hadith Graphs using Arabic Morphological Analysis}

@@

\begin{document}

\maketitle

\begin{abstract}
\end{list}
A hadith in Islamic literature is a narration from the 
prophet Mohammad related by multiple narrators.
Establishing the authenticity of a hadith is an important task
based on which Islamic scholars issue rules that affect the life
of people around the world. 
The literature lacks an automated and exhaustive mechanism of 
authentication checks. 
This is currently manual work prone to error and almost
impossible to complete in the life time of a scholar due to the
large literature available. 
In this paper, we present a tool that uses 
an Arabic application-specific morphological analyzer 
to successfully automate the
analysis of three books of hadith selected 
arbitrarily and abstract 
each book into a graph of narrators related to each other. 
\end{abstract}

\section{Introduction}

A \RL{.hady_t}~\footnote{In this document, 
we use the default ArabTeX transliteration style ZDMG.}
(tradition) 
is a narration related to the prophet Mohammad
through a \RL{sanad} or a sequence of narrators. 
The collections of traditions are the second source of
jurisprudence after the \RL{qor'An} for all Islamic schools of thought. 
Figure~\ref{f:exhadith} shows an example \noArRL{.hady_t} in 
Arabic with its transliteration and translation. 
We show proper names in boxes connected
to form complex names of narrators. 
For example, 
\novocalize
\noTrRL{qtybT} is the first name 
of narrator $n_1$, and 
\noTrRL{s`yd} is the name of his father as 
the word \noTrRL{bn} (son of) indicates. 
The sequence of names from $n_1$ to $n_5$ 
constitutes the \noArRL{sanad} 
of the \noArRL{.hady_t}. 
The second part of the \noArRL{.hady_t} is the 
\RL{matn} (content) and constitutes the actual content 
of the tradition.

@@

\novocalize

In this paper, we present the hadith {narrator graph
extractor using morphological analysis} (NaGEMA), 
a novel technique that automates
extracting the \noArRL{sanad} from the books of traditions 
into a diagram of chains of narrators. NaGEMA segments
a book into narrations, each narration into its \noArRL{matn} 
and its \noArRL{sanad}, 
and each sanad into its separate narrators. 
This work will lead to 
automate an exhaustive \noArRL{.hady_t} authentication 
effort in the future as we plan to 
automatically analyze the biography books.

@@

The morphological analysis of the word \RL{.hd_tnA} 
``narrated to us'' that starts the hadith in Figure~\ref{f:exhadith}
returns the stem \RL{.hd_t}.
The stem  \RL{.hd_t} is also the stem of other 
words such as \RL{.hd_tny} and \RL{.hd_thm}.
The stem also shares similar part of speech (POS)
and English meaning gloss annotations with words
such as \RL{qaal} ``said'' and \RL{'a_hbar} ``told''. 
The use of morphological analysis allows us to 
subsume listing these stems and all of their morphological
derivations with one rule that matches the gloss and 
POS tags. 
Similarly the words \RL{ibn} ``the son of'' and \RL{bn} 
return the same morphological analysis.

@@

%The rest of this paper is structured as follows. 
%In Section~\ref{sec:sarf}
%we discuss Sarf and illustrate it with a running example.
%We also explain how non-deterministic finite state Automata
%work. 
%In Section~\ref{sec:islamic} we present the hadith application. 
%We present our results in Section~\ref{sec:results}.
%In Section~\ref{sec:related}
%we compare NaGEMA to related work. 
%We conclude with future work in Section~\ref{sec:future}.

@@

%Several researchers~\cite{Hadithopaedia:08} attempted to automate 
%the analysis of the hadith literature. 
In this paper, we use Sarf to automate the
analysis of three books of hadith selected 
arbitrarily~\cite{IbnHanbal,AlKulayni,AlTousi}\footnote{We obtained
  the digitized books from online sources such as 
  \href{http://www.yasoob.com/}{http://www.yasoob.com/} and 
  \href{http://www.al-eman.com/}{http://www.al-eman.com/}. }.
%  Our understanding is that those books are historical documents with 
 % public IP.}.
%\setcode{utf8}
%\begin{arabtext}
%حدثنا \emphasize{هشيم}، أخبرنا \emphasize{إسماعيل بن أبي خالد}،
% عن أبي إسحاق، عن سعيد بن جبير، قال كنا
%    مع ابن عمر رضي الله عنه حيث أفاض من
%    عرفات إلى جمع فصلى بنا المغرب ومضى
%\end{arabtext}
%\setcode{standard}
NaGEMA accepts a book as input
and segments it into a vector of hadiths. 
NaGEMA segments each hadith into its
sanad and matn parts. 
NaGEMA 
detects the chain of narrators in the sanad and 
the relation that links each narrator to his ancestor and 
predecessor in the chain. 
It also detects the full name of each narrator that is
composed of several proper names with connectors
in between.

To do that NaGEMA queries Sarf for the following morphological 
categories.
\begin{itemize}
\item $\mathit{NAME}$: a proper name of a person such as \RL{'a.hmad} .
\item $\mathit{IBN}$: a special name connector meaning the son of such as \RL{ibn}.
\item $\mathit{NMC}$: other name connectors. 
\item $\mathit{NISBA}$: a possessive adjective that qualifies a person such 
as \RL{alma.sriy} ``the Egyptian''. 
\item $\mathit{NRC}$: a narrator connector such as
\RL{`an} ``on behalf of'', \RL{.hada_t} ``narrated'', \RL{qaal} ``said'', 
\RL{'a_hbar} ``told'' or one of their morphological equivalents. 
\end{itemize}

\begin{figure*}
\center{
\resizebox{1.9\columnwidth}{!}
{\includegraphics{figs/detailed_submachine.pdf}
}
\caption{The chain of narrators extractor diagram}
\label{f:chain}
}
\end{figure*}

The diagram in Figure~\ref{f:chain} describes 
the chain extraction process. 
We pass the hadith to the morphological analyzer 
and check the returned words and category pairs 
for name categories.
Next we compute the number of words between every two names
and compare that to a threshold $\theta_1$.
If the name is within the threshold we add it to a temporary 
chain of names. 
Otherwise, we 
{\bf 1.} tabulate the chain into a temporary table containing 
the list of chains and
{\bf 2.} Create a new chain with the last element.
Finally, we filter out those chains whose cardinality 
is less than some threshold  $\theta_2$.

The process also benefits from name connector 
words and narrator connector words to enhance the
accuracy of the chain extraction and to segment the 
chain accurately into narrators.
Once we meet a name connector or a narrator 
connector word we reset the word counters that we
compare against the thresholds. 
that directly interacted with Sarf.

@@

We implemented our hadith chain extraction 
in an finite state machine
controller that interfaces with Sarf.
Intuitively, the controller reports a valid chain 
of narrators when a sequence of names
connected by narrator connectors appears. 
%This includes the task of finding multi-word names
%such as \RL{`bd alr.hmn} often appearing as ``run-on'' words.
The controller marks the beginning of the hadith with 
the beginning of 
the current proper name sequence,
and marks the end of the hadith with the beginning of the 
next proper name sequence. 
It detects the chain of narrators as the sequence itself.

%The controller also targets words that mean ``narrate'' when
%they appear between proper names. 
We illustrate the hadith controller 
in Figure~\ref{f:hadith}. 
The transitions are labeled using expressions
that operate on the output tags 
generated from the Sarf morphological analyzer.

The controller has four states that correspond to 
a position in text relative to the next sanad. 
State $\mathit{TEXT\_S}$ is the initial state and denotes 
that the controller is outside the context of a sanad.
State $\mathit{NAME\_S}$ denotes that the controller is in
the middle of a chain and has last met a name. 
State $\mathit{NMC\_S}$ denotes that the controller is in
the middle of a narrator name.
State $\mathit{NRC\_S}$ denotes that the controller is 
in the context of a narrator name and the controller 
has met a narrator connector and is ready to meet 
a new narrator.

The threshold $\theta_{\mathit{nmc}}$ 
corresponds to the number of tolerated name connectors 
that may occur between two names. %3
The symbol $\mathit{LIST}_{\mathit{nmc}}$ corresponds to the list 
of name connectors collected since the controller
started looping in the state $\mathit{NMC\_S}$.
The symbol $\lambda_{\mathit{nmc}}$ is a parameter 
that corresponds to a relaxed tolerance measure that
the controller resorts to in case the words separating
two names were longer than $\theta_{\mathit{nmc}}$ but 
contained a name connector word such as $\mathit{IBN}$ 
or $\mathit{NISBA}$.

The controller moves to state $\mathit{NAME\_S}$ on
$\mathit{NAME}$.
It moves to state $\mathit{NRC\_S}$ 
when Sarf reports an $\mathit{NRC}$.
State $\mathit{NMC\_S}$
indicates that the controller expects a name to appear within 
a tolerance threshold expressed by 
$\theta_{\mathit{nmc}}$ and $\lambda_{\mathit{bmc}}$.
It returns to $\mathit{NAME\_S}$ when a name is met, 
loops when still within the threshold, and 
resets to $\mathit{TEXT\_S}$ when the threshold is exceeded 
signaling that the last collection of names met do not qualify
as a narrator or a chain or narrators.

Similarly, $\mathit{NRC\_S}$ tolerates $\theta_{\mathit{nrc}}$ words 
before it gives up on its expectations. 
Note that we reach the $\mathit{NAME\_S}$
state only when a
valid $\mathit{NAME}$ is detected and we leave when no 
more $\mathit{NAME}$'s are detected.
The $\mathit{NRC\_S}$ state can only be reached if an 
$\mathit{NRC}$ is detected.
The state $\mathit{NMC\_S}$ can only be reached from a 
$\mathit{NAME\_S}$ state.
We used the values of 3, 5 and 5 for $\theta_{\mathit{nmc}}$, 
$\lambda_{\mathit{nmc}}$, and 
$\theta_{\mathit{nrc}}$ respectively to run the experiments 
we report in Section~\ref{sec:results}.

@@

\begin{figure}[tb]
\center{
\resizebox{1.1\columnwidth}{!}
%{\includegraphics{figs/narrator_chain_output.pdf}}
{\includegraphics{figs/DAG_narrator.pdf}}
\caption{Narrator directed acyclic graph 
    extracted using NaGEMA }
\label{f:narrators} 
}
\end{figure}

The directed acyclic graph (DAG) 
in Figure~\ref{f:narrators} shows a partial order relation (POR) 
between narrators.
We automatically extracted the POR from the three books of 
hadith~\cite{IbnHanbal,AlKulayni,AlTousi}.
The nodes in boxes are the \RL{matn} of the hadith, 
and the other nodes are the narrators.
Given a set of chains of narrators similar to 
Figure~\ref{f:exhadith} we formed the DAG using graph algorithms 
that merged equal names in the chains. 
We compared the narrators together using a morphological
distance function. 
We considered each narrator to have several morphological 
components and we rewarded every morphological match with 
a small $\delta$. 
Then we applied a threshold $\theta$ to the sum of rewards
and decided the equality of the narrators. 
%We omitted the details of the distance function for brevity.

\begin{table}[tb]
%\centering
%\resizebox{.9\columnwidth}{!}{
\begin{tabular} {p{6cm}}
\begin{Verbatim}[fontsize=\relsize{-2},
frame=topline,framesep=4mm,label=\fbox{MergeChains algorithm},
commandchars=\\\{\}, codes={\catcode`$=3\catcode`_=8}]
Merge(Chain $C$[])
  Chain $C_c$[]=\{\}
  foreach Chain $c_1$ in $C$ 
    $C_c = C_c \cup c_1$
    foreach Narrator $n_1$ in $c_1$
      foreach Chain $c_2$ in $C-C_c$
        foreach narrator $n_2$ in $c_2$

    \}
  \}
\end{Verbatim}
\end{tabular}
%}
\label{a:merge}
\end{table}

\subsection{Graph merge Algorithm}

\begin{table}[tb]
%\centering
%\resizebox{.9\columnwidth}{!}{
\begin{tabular} {p{6cm}}
\begin{Verbatim}[fontsize=\relsize{-2},
frame=topline,framesep=4mm,label=\fbox{Narrator distance metric },
commandchars=\\\{\}, codes={\catcode`$=3\catcode`_=8}]
Distance(Narrator n1, Narrator n2)
  $N_1$ = stems(n1.names)
  $N_2$ = stems(n2.names)

  $I_1$ = extractIbn( stems(n1.connectors) )
  $I_2$ = extractIbn( stems(n2.connectors) )

  $C_1$ = stems(n1.connectors - $I_1$)
  $C_2$ = stems(n2.connectors - $I_2$)

  $E_n$ = getEqualNames($N_1$, $N_2$)
  if ( $E_n$.isEmpty ) 
      return $\infty$
  if ( $E_n$.size $\ge$ min($N_1$.size,$N_2$.size))
    dist -= $\delta_1$
  if ($E_n$.equalNamesInOrder())  
    dist -= $\delta_2$

  if ($C_1 \cap$ Places $\not= C_2 \cap$ Places)
    dist += $\delta_3$
  else
    dist -= $\delta_3$

  $E_c$ = getEqualConnectors($C_1$, $C_2$)
  dist -= $E_c$.size * $\delta_4$

  if (correctIbnCorrespondence($I_1$, $I_2$))
      dist -= $\delta_5$
  return (MAX - dist)
\end{Verbatim}
\end{tabular}
%}
\label{a:distance}
\end{table}

\subsection{Narrator morphological distance metric}

\subsection{Use of the POR graph}

inconsistency check 
consistency checks
annotate with information extracted from biographies
what if analysis

@@

We ran our experiments using a dual core 2.66 Ghz 64-bit processor 
with 4GB of memory using a Linux operating system. 
We report our results in Table~\ref{t:hadithresallresults} on the 
three hadith books.
NaGEMA detected narrator chains and segmented the books 
correctly with a chain accuracy above 97\% and a narrator name
accuracy above 90\%
in all cases and across all the 1986 traditions in the three 
different books with different formats.

@@

The ``segmentation accuracy'' reports on the accuracy of 
segmentation of the book into separate hadiths.
We computed the metric manually by marking the beginning 
and end of a representative sample of hadiths in each 
book and compared that to the NaGEMA results. 
We used the same approach to compute all other accuracy measures.
The ``chain accuracy'' reflects the percentage of correct narrators 
covered by extracted chains.
The ``narrator name accuracy'' row reflects the percentage of 
correct proper names detected within
narrator structures.

@@

NaGEMA does not need a preprocessing step since 
it uses morphological analysis to process the text. 
While e-Narrator bases its analysis on the patterns 
of words that surround the narrator names, 
NaGEMA bases its analysis on the fact that narrator
names are likely to happen in localities with a high
number of proper names. 
NaGEMA uses the narrator connectors as helpers and
uses morphological analysis to compare the stems of
those words and thus NaGEMA avoids the problem of 
``parser noise words'' that e-Narrator faces. 
Even though we do not have access to the selected
90 traditions e-Narrator reports on, we claim
that NaGEMA outperforms e-Narrator as it works on
the full text of the presented hadith books
and reports a higher success rate.

@@

We presented NaGEMA, a narrator chain extractor
using morphological analysis. 
NaGEMA extracted narrator chains with above 90\% accuracy
from three different hadith books and generated 
directed acyclic graphs relating the narrators 
in a partial order relation.
